\documentclass[a4paper,11pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[top=2cm,bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{siunitx}
\setlength{\parindent}{0pt}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{subfiles}
\usepackage[numbers]{natbib}
\usepackage{amsmath}
\usepackage{float}

%figures and subfigures
\usepackage{caption}
\usepackage{subcaption}

\usepackage{setspace}
\onehalfspacing

\usepackage[toc,page]{appendix} %allows fancyhdr and notoccite together
\usepackage{notoccite} %references in captions numbering

\usepackage{fancyhdr}
\fancypagestyle{main}{%
  \fancyhf{}
  \fancyhead[L]{\nouppercase{\leftmark}}%
  \fancyhead[R]{Page \thepage}%
  \renewcommand{\headrulewidth}{0.5pt}%
  \setlength{\headheight}{14pt}
  \setlength{\headsep}{15pt}
  \addtolength{\topmargin}{15pt}
}

\sisetup{per-mode = symbol}




\title{FYP}
\author{Luca Mazzotta}
\date{May 2023}


\begin{document}



\pagestyle{plain}
\pagenumbering{roman}

\input{LaTeX/titlepage}
\newpage

\begin{abstract}
    \noindent{Given the recent increase in interest in space exploration and the relevance of rarefied hypersonics in the development of the next generation entry vehicles, a research into the effects of global and local Knudsen number on heat transfer was deemed worth to pursue. The theoretical background for rarefied flow was outlined, and relevant research in the field was examined. It was concluded that the optimal simulation method to carry out said research was Direct Simulation Monte Carlo. The method was thus explored, and four sets of simulations were designed: varying global Knudsen number, varying edge radius, varying angle of attack and constant local Knudsen number. The simulation were designed around simple geometries, such as circles and squares, in order to limit the number of variables. Convergence studies were thus carried out and the simulation results validated. From the simulations a drastic change in flow physics with rarefaction was noted, and a theoretical explanation was provided. Moreover, the dependence of the ratio between the peak and stagnation Stanton numbers on a cube with Knudsen number were investigated. No conclusive evidence was however found, and the need for further studies was pointed out.}
\end{abstract}
\newpage

\renewcommand{\abstractname}{Ringraziamenti}
\begin{abstract}
\noindent{Ai miei genitori e ai miei nonni, a cui desidero esprimere la mia gratitudine per l'amore e l'attenzione dedicati nel trasmettermi il valore della perseveranza e dell'impegno.}
\end{abstract}
\newpage

\tableofcontents
\newpage

\addcontentsline{toc}{section}{List of Figures}
\listoffigures
\newpage

\addcontentsline{toc}{section}{List of Tables}
\listoftables
\newpage

\pagestyle{main}
\pagenumbering{arabic}



\input{LaTeX/1. Introduction}
\newpage

\input{LaTeX/2. Background}
\newpage

\input{LaTeX/3. Methodology}
\newpage

\input{LaTeX/4. Results}
\newpage

\input{LaTeX/5. Conclusion}
\clearpage

{\small
\bibliographystyle{unsrtnat}
\bibliography{export}
}

\end{document}
